### 2014-07-01 tex/main-body-text.tex
Fit Fig 2 into a single column.
Note that I pdfcropped Fig2.pdf to squeak a few more mm out of it.
Changed k to K

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
{\sc flock} still produces estimates of the LLOD by individual for the 
'best run', however, it is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

@@

\begin{figure}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=25em]{images/Figures-Pat/Fig2.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{fig:qscatter}
\end{center}
\end{figure}

To investigate the ability of the arrangement of individuals within the reference 
populations to move around the partition space we varied the number of iterations that 
each run goes through to find the 'optimal' allocation of individuals. Unfortuantely 
only the reallocation matrix for the 'best run' is given as output. Increasing the 
number of iterations did not affect the overall inference of \textit{k}. We 
observed that often during the last iterations individuals would alternate between 
reference groups. Increasing the log likelihood 
difference threshold for reallocation to 0.18 (requiring at least a 1.5 times 
higher likelihood to reallocate the individual) minimized this, but did not affect the 
inference of \textit{k} (lower bound estimate of \textit{k} = 2).

@@

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, 'The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each \textit{k}'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each \textit{k} = 1 to K+4. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of \textit{k} from 1 to K+3. 
It seemed reasonable to compare, for each \textit{k}, one iteration of {\sc structure} 
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both evaluate the partition space once. The dataset used in this comparision was an order of magnatude
larger than the largest used by \citep{Duc&Tur2012} (N = 60, 120, and 240). Any process speed advantages 
may only been observed with small sample sizes.

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind, $k$ is the number of clusters, and $n$ is the number of individuals.
The likelihood surface spanning all possible partitions
may be characterized by multiple peaks and troughs.
The peak or plateau that the  {\sc flock} algorithm finds is entirely dependent on the initial allocation of 
individuals as it has no way to visit areas of the likelihood surface with smaller values.
 It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as \textit{k} increases
{\sc flock} finds suboptimal allocations. If the number of initial allocations does not increase
as $K$ is increased, the starting allocations become diffusely scattered in the space of all
possible partitions making it unlikely that they will converge.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in {\sc structure} \citep{Evannoetal2005, 
Pritchardetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, much less effort has been put forth examining how the number of individuals
and thenumber of starting allocations can affect not only the convergence of different runs, but also the 
inference of $K$. The authors developed estimation rules based on simulated data 
sets with a modest number of individuals and different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular \textit{k},  similar but not idential 
allocations will provide no support to a given \textit{k}.

>>>>

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for $K = 2$ to 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
$K$ increases so do the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
{\sc flock} still produces estimates of the LLOD by individual for the 
'best run', however, it is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

@@

\begin{figure}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=\columnwidth]{images/Figures-Pat/Fig2.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for $K=5$. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{fig:qscatter}
\end{center}
\end{figure}

To investigate the ability of the arrangement of individuals within the reference 
populations to move around the partition space we varied the number of iterations that 
each run goes through to find the 'optimal' allocation of individuals. Unfortuantely 
only the reallocation matrix for the 'best run' is given as output. Increasing the 
number of iterations did not affect the overall inference of $K$. We 
observed that often during the last iterations individuals would alternate between 
reference groups. Increasing the log likelihood 
difference threshold for reallocation to 0.18 (requiring at least a 1.5 times 
higher likelihood to reallocate the individual) minimized this, but did not affect the 
inference of $K$ (lower bound estimate of $K = 2$).

@@

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, ``The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each $K$ from 1 to four more than 
the true value of $K$. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to K+3. 
It seemed reasonable to compare, for each $K$, one iteration of {\sc structure} 
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both evaluate the partition space once. The dataset used in this comparision was an order of magnatude
larger than the largest used by \citep{Duc&Tur2012} (N = 60, 120, and 240). Any process speed advantages 
may only been observed with small sample sizes.

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind, $k$ is the number of clusters, and $n$ is the number of individuals.
The likelihood surface spanning all possible partitions
may be characterized by multiple peaks and troughs.
The peak or plateau that the  {\sc flock} algorithm finds is entirely dependent on the initial allocation of 
individuals as it has no way to visit areas of the likelihood surface with smaller values.
 It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as $K$ increases
{\sc flock} finds suboptimal allocations. If the number of initial allocations does not increase
as $K$ is increased, the starting allocations become diffusely scattered in the space of all
possible partitions making it unlikely that they will converge.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in {\sc structure} \citep{Evannoetal2005, 
Pritchardetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, much less effort has been put forth examining how the number of individuals
and thenumber of starting allocations can affect not only the convergence of different runs, but also the 
inference of $K$. The authors developed estimation rules based on simulated data 
sets with a modest number of individuals and different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular $K$,  similar but not idential 
allocations will provide no support to a given $K$.
